\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-09 ms.tex
photo calib

% Edits
\newcommand{\changes}[1]{{\ \color{red}{\textbf{#1}\ }}}
\newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}

@@

We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.
At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
The measured distance is inconsistent with stream predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by its the last disk midplane passage. % at a Galactocentric radius $R \approx 30~\kpc$.
Most details of this idea remain a puzzle: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
This cluster was discovered with \gaia\ astrometry and photometry alone, but folow-up \decam\ photometry was crucial for measuring its properties.
\end{abstract}

@@

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.  The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for global zero-point and color-terms in each band.

@@

>>>>

% Edits
\newcommand{\changes}[1]{{\ \color{black}{\textbf{#1}\ }}}
\newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}

@@

\changes{We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.}
At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
The measured distance is inconsistent with stream predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by its the last disk midplane passage. % at a Galactocentric radius $R \approx 30~\kpc$.
Most details of this idea remain a puzzle: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
This cluster was discovered with \gaia\ astrometry and photometry alone, but folow-up \decam\ photometry was crucial for measuring its properties.
\end{abstract}

@@

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.

\changes{The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and
with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}

@@

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation Equations}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term} & \colhead{RMS}
}
\startdata
$u$  &  $g-i$ & 2.17820 $\pm$   0.016 &     \nodata  & 0.164 \\
$g$  & $g-r$ & $-$0.052868 $\pm$  0.0068  &     $-$0.034937 $\pm$   0.0051  &  0.028 \\
$i$   &  $i-z$ & $-$0.246645 $\pm$  0.0011 &     $-$ -0.07379 $\pm$   0.00069  &  0.028  \\

\enddata
\label{table_transphot}
\end{deluxetable}
\end{center}
